---
title: "Simple FSPM Model"
author: "Guillaume"
date: "9/6/2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=F, warning=F, message=F}
source("contructor_functions.R")

# Initiate the parameters
params <- plantParameters()
params$root_growth_rate <- 0.8
params$root_branching_age <- 3

# Initiate the plant
pl <- plant()
pl <- addNodeToPlant(pl, node(1,0, parent=0, id=1, type="seed", organ_id = 1))
pl <- addNodeToPlant(pl, node(1,-1, parent=1, id=2, type="root", organ_id = 2))
pl <- addNodeToPlant(pl, node(1,1, parent=1, id=3, type="stem", organ_id = 3))
params$max_id <- 3
params$max_organ_id <- 3
# Grow the plant
max_time = 20
for(i in c(1:max_time)){
  # Update the time of the simulation
  params$current_time <- i
  params$flower_number <- 0
  
  # Count the number of flowers in the network
  for(j in c(1:length(pl$nodes))){
    if(pl$nodes[[j]]$type == "flower"){
      params$flower_number  <- params$flower_number +1
      if(pl$nodes[[j]]$diameter < params$flower_max_diameter){
        pl$nodes[[j]]$diameter <- pl$nodes[[j]]$diameter + params$flower_growth_rate
      }
    }
  }
  
  # Grow the different nodes in the plant
  for(j in c(1:length(pl$nodes))){
    pl$nodes[[j]]$age <- pl$nodes[[j]]$age + 1
    if(pl$nodes[[j]]$growing){
      pl <- growNode(pl, pl$nodes[[j]], time=1, params = params)
      pl$nodes[[j]]$growing <- F
      params$max_id <- params$max_id + 1
    }
  }
  
  # Branch the different nodes in the plant
  for(j in c(1:length(pl$nodes))){
    if(pl$nodes[[j]]$type == "root"){
      if(pl$nodes[[j]]$branching & pl$nodes[[j]]$age > params$root_branching_age){
        pl <- branchNode(pl, pl$nodes[[j]], params = params)
        pl$nodes[[j]]$branching <- F
        params$max_id <- params$max_id + 1
        params$max_organ_id <- params$max_organ_id + 1
      }
    }else if(pl$nodes[[j]]$type == "stem"){
      if(pl$nodes[[j]]$branching & pl$nodes[[j]]$age > params$stem_branching_age){
        pl <- branchNode(pl, pl$nodes[[j]], params = params)
        pl$nodes[[j]]$branching <- F
        params$max_id <- params$max_id + 1
        params$max_organ_id <- params$max_organ_id + 1
        params$leaf_number <- params$leaf_number + 1
        params$leaf_orientation <- - params$leaf_orientation
      }
    }
  }
}

```



```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("colour", "Colour to plot", choices = c("type", "id", "organ_id", "age")),
  sliderInput("time", label = "Time to plot",
              min = 1, max = 20, value = 1, step = 1)
)

renderPlot({

 rs <- tibble(x = map(pl$nodes, "x"),
               y = map(pl$nodes, "y"),
               diameter = map(pl$nodes, "diameter"),
               type = map(pl$nodes, "type"),
               id = map(pl$nodes, "id"),
               organ_id = map(pl$nodes, "organ_id"),
               age = map(pl$nodes, "age"),
               order = map(pl$nodes, "order"),
               parent = map(pl$nodes, "parent"),
               creation = map(pl$nodes, "creation_time")) %>% 
    unnest()
  
  rs$x1 <- rs$x
  rs$y1 <- rs$y
  for(i in c(2:nrow(rs))){
    rs$x1[i] <- rs$x[rs$id == rs$parent[i]]
    rs$y1[i] <- rs$y[rs$id == rs$parent[i]]
  }
  
  colour <- input$colour
  rs$var <- rs[[colour]]
  rs <- rs %>% filter(rs$creation < input$time)
  if(colour == "organ_id" | colour == "order") rs$var = factor(rs$var)
  ggplot(rs, aes(x, y, colour=var, size=diameter)) + 
    coord_fixed()+
    guides(colour=guide_legend(title=colour)) + 
    geom_hline(yintercept = 0, colour="brown") + 
    geom_segment(aes(xend=x1, yend=y1), size=0.5) + 
    geom_point(data = rs[rs$type == "flower",], aes(size=diameter), alpha = 0.5)
  

})
```
